---
title: "p8105_hw1_kk3154"
author: "Kristen King"
date: "9/27/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

Creating a dataframe containing a random sample of size 10 from normal distribution, logical vector for whether the elements of the sample are >0, character vector of length 10, and factor vector (3-level) with length 10.

```{r, message = FALSE}
library(tidyverse)
```

```{r}
set.seed(4321)

hw1_p1_df = tibble(
  rand_samp = rnorm(10, sd = 1),
  vec_logical = rand_samp > 0,
  vec_char = c("This", "is", "hw", "1", "for", "BIST", "P8105", "fall", "2021", "semester"),
  vec_factor3 = factor(c("blue", "green", "blue", "red", "blue", "green", "green", "green", "red", "red"))
)

hw1_p1_df

```

Attempting to take the mean of each variable.

What works?

What doesn't?

```{r}

```

Applying the as.numeric function to the logical, character, and factor variables to convert to numeric data type.

NOT showing the results of this output.

What happens, and why? Does this help explain what happens when you try to take the mean?

```{r}
#results = hide?
```

## Problem 2

The palmerpenguins data was installed in the console only.

Now loading the penguins dataset:

```{r }
data("penguins", package = "palmerpenguins")



```

The penguins dataset contains ...

The mean flipper length is `r mean(pull(penguins, flipper_length_mm))` mm.
