---
title: "p8105_hw1_kk3154"
author: "Kristen King"
date: "9/27/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

Creating a dataframe containing a random sample of size 10 from a normal distribution, a logical vector for whether the elements of the sample are >0, a character vector of length 10, and a factor vector (3-level) with length 10.

```{r, message = FALSE}
library(tidyverse)
```

```{r}
set.seed(4321)

hw1_p1_df = tibble(
  rand_samp = rnorm(10, sd = 1),
  vec_logical = rand_samp > 0,
  vec_char = c("This", "is", "hw", "1", "for", "BIST", "P8105", "fall", "2021", "semester"),
  vec_factor3 = factor(c("blue", "green", "blue", "red", "blue", "green", "green", "green", "red", "red"))
)
```

Attempting to take the mean of each variable.

```{r}
mean(pull(hw1_p1_df, rand_samp))
mean(pull(hw1_p1_df, vec_logical))
mean(pull(hw1_p1_df, vec_char))
mean(pull(hw1_p1_df, vec_factor3))
```

It is possible to take the mean of the variable containing the random sample and the logical vector.

It is not possible to take the mean of the character vector or the factor vector - it returns an error message that the argument is not numeric or logical and returns an "NA" result. 

Now applying the as.numeric function to the logical, character, and factor variables to convert to numeric data type, without showing the results of this output:

```{r, results = FALSE, warning = FALSE}
mean(as.numeric(pull(hw1_p1_df, vec_logical)))
mean(as.numeric(pull(hw1_p1_df,vec_char)))
mean(as.numeric(pull(hw1_p1_df, vec_factor3)))
```
The as.numeric function did the following:

* converted the logical vector into a series of 0's and 1's where 0 = FALSE and 1 = TRUE

* converted the character vector into NA's when there are letters or letter/number combinations in the string or leaves it a number if the string contained only numbers

* converted the 3-level factor variable into the numbers 1-3.

After applying the as.numeric function, it is now possible to take the mean of the logical vector and the factor vector because they are represented by numbers now where math functions can be applied. 

It is still not possible to take the mean of the character vector because not all elements are numbers, some are NA. It gives the warning message "NAs introduced by coercion".

## Problem 2

The palmerpenguins data was installed in the console only.

Now loading the penguins dataset:

```{r }
data("penguins", package = "palmerpenguins")



```

The penguins dataset contains ...

The mean flipper length is `r mean(pull(penguins, flipper_length_mm))` mm.
